---
title: "Coding Assignment 1"
author: "Team 3"
date: "Due: 2021-09-29 23:59"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
# Put any packages you want here
library(readxl)
library(dplyr) # for pipe operator
library(gt) # for fancier tables
library(gtsummary) # for fancier summary statistics
library(corrplot) # for fancier correlations
library(car) # for easier scatterplots
library(jtools) # for fancier regression output
library(psych)
library(readr)
library(plotly)
 
```


A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


**For this assignment, ignore the categorical variables (gender, smoker, cities)**

```{r dataset, include=FALSE}
# Bring in the dataset here

insurance <- read.csv("../Data/insurance_0126_Group3.csv") 

str(insurance)

```



# Question 1

Perform univariate analyses on the quantitative variables (center, shape, spread). Include descriptive statistics, and histograms. Be sure to use terms discussed in class such as bimodal, skewed left, etc.

```{r q1}
describe(insurance)
summary(insurance)
```

#Center


##Mean
```{r mean}

mean(insurance$Charges)

mean(insurance$Age)

mean(insurance$BMI)

mean(insurance$Children)


```

##Median
```{r median}
median(insurance$Charges)

median(insurance$Age)

median(insurance$BMI)

median(insurance$Children)
```


##Mode
```{r mode}
getModes <- function(x) {
  ux <- unique(x)
  tab <- tabulate(match(x, ux))
  ux[tab == max(tab)]
}

getModes(insurance$Charges)

getModes(insurance$Age)


getModes(insurance$BMI)



getModes(insurance$Children)



```
Mode for Charges - No Mode 
Mode for Age - Unimodal
Mode for BMI - Trimodal 
Mode for Children - Unimodal


#Shape


##Histograms
```{r histogram}


hist(insurance$Charges, col = 5)

hist(insurance$Age, col = 3)

hist(insurance$BMI, col = 0)

hist(insurance$Children, col = 2)
```



#Spread
```{r spread}
describe(insurance)



var(insurance$Charges, na.rm = TRUE)
sd(insurance$Charges, na.rm = TRUE)
IQR(insurance$Charges, na.rm = TRUE)
range(insurance$Charges, na.rm = TRUE)


var(insurance$Age, na.rm = TRUE)
sd(insurance$Age, na.rm = TRUE)
IQR(insurance$Age, na.rm = TRUE)
range(insurance$Age, na.rm = TRUE)


var(insurance$BMI, na.rm = TRUE)
sd(insurance$BMI, na.rm = TRUE)
IQR(insurance$BMI, na.rm = TRUE)
range(insurance$BMI, na.rm = TRUE)


var(insurance$Children, na.rm = TRUE)
sd(insurance$Children, na.rm = TRUE)
IQR(insurance$Children, na.rm = TRUE)
range(insurance$Children, na.rm = TRUE)
```


##Histogram Plots and skews
```{r plots}
plot_ly(x = ~insurance$Charges, type = "histogram", alpha = 0.6) %>% 
  layout(title = 'Distribution of Insurance',
         xaxis = list(title = 'Charges'),
         yaxis = list(title = 'Count')) 
                                               


plot_ly(x = ~insurance$Age, type = "histogram", alpha = 0.6) %>% 
  layout(title = 'Distribution of Insurance',
         xaxis = list(title = 'Age'),
         yaxis = list(title = 'Count'))
         
                                                                                     
plot_ly(x = ~insurance$BMI, type = "histogram", alpha = 0.6) %>% 
  layout(title = 'Distribution of Insurance',
         xaxis = list(title = 'BMI'),
         yaxis = list(title = 'Count'))
                                                

                                                
plot_ly(x = ~insurance$Children, type = "histogram", alpha = 0.6) %>% 
  layout(title = 'Distribution of Insurance',
         xaxis = list(title = 'Children'),
         yaxis = list(title = 'Count'))
                                                


```
Data for Charges is Skewed left
Data for Age skewed to the left but only a little
Data for BMI is almost symmetrical
Data For Children is Skewed left

# Question 2

Perform bivariate analyses on the quantitative variables (direction, strength and form). Describe the linear association between all variables. 

```{r q2}
cor(insurance)
reduced <- insurance %>%
  select(Charges, Age, BMI, Children)

corrplot(cor(reduced),
type = "lower",
order = "hclust",
tl.col = "black",
tl.srt = 45,
addCoef.col = "black",
diag = FALSE)

```

# Question 3

Generate a regression equation in the following form:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children$$

```{r q3}

model <- lm(Charges ~ Age + BMI + Children, data = insurance)
summary(model)


summ(model)


```

also write out the regression cleanly in this document.

Regression Equation is: 
Charges = -18209.91 +11.52(Age) + 1067.17(BMI) + 1290.77(Children)

# Question 4

An eager insurance representative comes back with a potential client. The client is 40, their BMI is 30, and they have one dependent. Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)


```{r q4}


newPrediction <- data.frame(Age = 40,
BMI = 30,
Children = 1)
predict(model, newdata = newPrediction)




model$coefficients["Age"]

model$coefficients["BMI"]

model$coefficients["Children"]


predict(model, newdata = newPrediction, interval = "confidence", level = .95)

```