---
title: "Coding Assignment 1"
author: "Team N"
date: "Due: 2021-09-29 23:59"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages}
# Put any packages you want here
Vanessa - do we really need any packages? Shouldn't they already be in our programs? readexcel? 
```


A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


**For this assignment, ignore the categorical variables (gender, smoker, cities)**

```{r dataset, include=FALSE}
# Bring in the dataset here
Vanessa - readexcel(location of data), describe the column types with col_types = c(descriptions)

```



# Question 1

Perform univariate analyses on the quantitative variables (center, shape, spread). Include descriptive statistics, and histograms. Be sure to use terms discussed in class such as bimodal, skewed left, etc.

```{r q1}
Vanessa: name the file 
summary(filename) -- this will give us basic statistics like mean median and Q1,Q3
hist(filename) - will produce a histogram

```

# Question 2

Perform bivariate analyses on the quantitative variables (direction, strength and form). Describe the linear association between all variables. 

```{r q2}
vanessa: 
plot(x - 1st variable,y-2nd variable), type=l for the line Main = "title" of graph xlab = "xaxis title" ylab = "yaxis title"  for a scatter plot
```

# Question 3

Generate a regression equation in the following form:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children$$

```{r q3}
Vanessa: name the model then the formula is lm(dependent variable ~ independent variable, data = name)
summary(model we named) will give us SEE if we want to find the correlation cor(filename$independant variable,filename$dependent variable)^2 
```

also write out the regression cleanly in this document.

# Question 4

An eager insurance representative comes back with a potential client. The client is 40, their BMI is 30, and they have one dependent. Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)


```{r q4}
vanessa:  set up the newprediction data.frame(variable =#,variable =#,variable =#) then we need to run the prediction predict(name of our model,newdata=newprediction) --this will plug in the values and spit out the answer FOR the confidence interval we want to use the same function as above and write interval an the decimal we want predict(name of our model,newdata=newprediction, interval = "confidence", level =.95)
                                                ```