---
title: "Coding Assignment 2"
author: "Team 3"
date: "Due: 2021-10-23 23:59"
output: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
#Put any packages you need here

library(readxl)
knitr::opts_chunk$set(echo = TRUE)
```

A Florida health insurance company wants to predict annual claims for individual clients. The company pulls a random sample of 50 customers. The owner wishes to charge an actuarially fair premium to ensure a normal rate of return. The owner collects all of their current customer’s health care expenses from the last year and compares them with what is known about each customer’s plan. 

The data on the 50 customers in the sample is as follows:

-	Charges: Total medical expenses for a particular insurance plan (in dollars)
-	Age: Age of the primary beneficiary
-	BMI: Primary beneficiary’s body mass index (kg/m2)
-	Female: Primary beneficiary’s birth sex (0 = Male, 1 = Female)
-	Children: Number of children covered by health insurance plan (includes other dependents as well)
-	Smoker: Indicator if primary beneficiary is a smoker (0 = non-smoker, 1 = smoker)
-	Cities: Dummy variables for each city with the default being Sanford

Answer the following questions using complete sentences and attach all output, plots, etc. within this report.


```{r dataset, include=FALSE}
insurance <- read.csv("../Data/insurance_0126_Group3.csv")
```



## Question 1

Generate this regression equation:

$$Charges = \beta_{0}+\beta_{1}*Age+\beta_{2}*BMI+\beta_{3}*Children + \beta_{4}*Female + \beta_{5}*Smoker + \beta_{6}*WinterSprings + \beta_{7}*WinterPark + \beta_{8}*Oviedo$$

```{r q1}
model <- lm(Charges ~ Age + BMI + Children + Female + Smoker + WinterSprings + WinterPark + Oviedo, data = insurance)
summary(model)



```

Which independent variables test significant in a two-tailed test? Use $\alpha = 0.2$

 At a two-tail test @ alpha =.2, Age , BMI, Children, and Smoker are the independent variables that tested significant.

Age P value = .0111 < alpha .2
BMI P value = .0286 < alpha .2
Children P value = .0008 < alpha .2
Smoker P value = 5.56e-16 < alpha .2

## Question 2

Interpret the coefficients of all the independent variables that tested significant.


Since Age, BMI, Children, and Smoker are the only ones that tested significant at the 80% level, let's analyze the coefficients. 

If a person's Age increases by 1, Charges are approximately expected to increase by 135 dollars, give or take 77 dollars. 

If a person's BMI increases by 1, Charges are approximately expected to increase by 571 dollars, give or take 205 dollars. 

If  Children increases by 1, Charges are approximately expected to increase by 1259 dollars, give or take 990 dollars. 

If Smoker increases by 1, Charges are approximately expected to increase by 24436 dollars, give or take 2469 dollars. 


## Question 3

The insurance agent returns with another client:

- Age: 35
- BMI: 26
- Children: 1
- Gender: Female
- Smoker: No
- City: Sanford

Using the regression equation above, predict the amount of medical expenses associated with this policy. (Provide a 95% confidence interval as well)

```{r q3}

newPrediction <- data.frame(Age = 35,
BMI = 26, Female = 1, Smoker = 0,
Children = 1, WinterSprings = 0, WinterPark=0, Oviedo =0)
predict(model, newdata = newPrediction)




model$coefficients["Age"]

model$coefficients["BMI"]

model$coefficients["Children"]


predict(model, newdata = newPrediction, interval = "confidence", level = .95)
```
We are 95% confident for this new policy holder at Age 35, BMI at 26, with 1 Child, Female, not a Smoker, living in Sanford  will be expected to be charged between $3848.788 and $11298.29



## Question 4

Compare the model from question 1, to a model that does not include the group of city dummies. Does including the cities reduce the SSE by a statistically significant amount? (check the partial F-test for significance of the dummies as a group). Use $\alpha = 0.05$

```{r q4}
reduced_insurance <- insurance[,-(7:9)] # drops last 3 columns
model_insurance <- lm(Charges ~. , data = reduced_insurance)
summary(model_insurance)



anova(model_insurance, model)
```
Removing the cities did not have a significant impact in the insurance charges as the F score of .6956 is not less than the alpha of .05.

